When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-12-12 doc/agu_2017/vpd.tex
starting final edits for AGU
some small progress

\documentclass{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

@@

\title[Your Short Title]{When does vapor pressure deficit drive or reduce evapotranspiration?}
\author{Adam Massmann,  Pierre Gentine and Changjie Lin}
\institute{AGU Fall Meeting (Rough Draft)}
\date{December 14th, 2017}

@@

\section{Introduction}
\begin{frame}{Does VPD drive or reduce ET? - hydrometeorologists' perspective}
  \begin{Huge}
  \[VPD = (1-RH)\cdot e_s (T)\]
\end{Huge}
  \begin{itemize}
  \item \textbf{Hydrometeorologists} would say that an increase in VPD (increase in \textbf{atmospheric demand}) would drive an \textbf{increase in ET}.
  \end{itemize}
\end{frame}

\begin{frame}{Does VPD drive or reduce ET? - physiologists' perspective}
  \begin{figure}
  \includegraphics[width=2.25in]{stomata.png}% was O(1.5in)
  \caption{from evolution.berkeley.edu}
\end{figure}
  \begin{itemize}
  \item However, \textbf{plant physiologists} know that plants have evolved to use stomata to conserve and regulate water use. So \textbf{stomata closure} in response to increases in VPD may \textbf{decrease ET}.
  \end{itemize}
\end{frame}

\begin{frame}{The question is, which effect dominates with an increase in VPD: plant response (decrease in ET) or atmospheric demand (increase in ET)?}
  \begin{itemize}
  \item It should be a function of plant type and the environment:
    \begin{itemize}
    \item Plants that are evolved to conserve water will tend to reduce ET with increases in VPD.
    \item However the environment can overwhelm plant response: at some threshold (i.e. very high VPD) the atmospheric demand should dominate and plants will not be able to conserve water, no matter how much they have evolved to do so.
    \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\documentclass[aspectratio=169]{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

@@

\title[Your Short Title]{When does vapor pressure deficit drive or reduce evapotranspiration?}
\author{Adam Massmann,  Pierre Gentine and Changjie Lin}
\institute{AGU Fall Meeting}
\date{December 14th, 2017}

@@

\section{Introduction}
\begin{frame}{Does VPD drive or reduce ET? - atmospheric demand perspective}
  \begin{Huge}
  \[VPD = (1-RH)\cdot e_s (T)\]
\end{Huge}
  \begin{itemize}
  \item Increase in VPD (\textbf{increase in atmospheric demand}) drives  an \textbf{increase in ET}.
  \end{itemize}
\end{frame}

\begin{frame}{Does VPD drive or reduce ET? - plant response perspective}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item However, plants evolved to use stomata to conserve and regulate water use. So \textbf{stomata closure} in response to increases in VPD may \textbf{decrease ET}.
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=2.25in]{stomata.png}% was O(1.5in)
        \caption{from evolution.berkeley.edu}
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{The question is, which effect dominates with an increase in VPD: plant response (decrease in ET) or atmospheric demand (increase in ET)?}
  \begin{itemize}
  \item Apriori intuition:
    \begin{itemize}
    \item Should be a function of plant type. e.g. plants that are evolved to conserve water will tend to reduce ET with increases in VPD.
    \item But the environment still matters: if the atmosphere dries enough  e.g. in very dry conditions the plants will not be able to conserve water, no matter how much they have evolved to do so.
    \end{itemize}
  \end{itemize}
\end{frame}
